Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-25 snapshot_system/snapshot.tex
inserted b bu numbers

Let $b$ be the total number of data chunks after localized deduplication, 
$b_u$ be the total number of fingerprints 
in the global index after complete deduplication, and
$C_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $C_i = \frac{C_1}{i^\alpha}.$
Since $ \sum_{i=1}^{b_u}C_i = b$,
\[
C_1 \sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
\]
Given $\alpha <1$, $C_1$ can be approximated with integration:
\begin{equation}
C_1=\frac{b(1-\alpha)}{b_u^{1-\alpha}}.
\end{equation}

>>>>

{\it [Need to find a place to put these numbers in: Total number of chunks in 350 snapshots: 1,546,635,485. Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
Let $b$ be the total number of data chunks after localized deduplication, 
$b_u$ be the total number of fingerprints 
in the global index after complete deduplication, and
$C_i$ be the frequency for the $i$th most popular fingerprint. 
By Zipf-like distribution, $C_i = \frac{C_1}{i^\alpha}.$
Since $ \sum_{i=1}^{b_u}C_i = b$,
\[
C_1 \sum_{i=1}^{b_u}\frac{1}{i^\alpha} = b
\]
Given $\alpha <1$, $C_1$ can be approximated with integration:
\begin{equation}
C_1=\frac{b(1-\alpha)}{b_u^{1-\alpha}}.
\end{equation}
